### 2010-03-19 doc/manuals/configuration/configuration_manual.tex
Removing schemas from configuration manual, as these can now be found at http://www.nordugrid.org/schemas/.
Specifying default values for configuration options.

\begin{tabular}{>{\ttfamily}l>{\ttfamily}l}
\toprule
\textrm{\textbf{XML element/attribute}} & \textrm{\textbf{INI tag}} \\
\midrule
/Server/PidFile & pidfile \\
/Server/User & user \\
/Server/Group & group \\
/Server/Logger/File & logfile \\
/Server/Logger/Level & loglevel \\
/Server/Logger/Maxsize & logmaxsize \\
/Server/Logger/Backups & logbackups \\
\midrule
\multicolumn{2}{c}{\textbf{TCP MCC}}\\
\midrule
/Component/Listen/Interface & interface \\
/Component/Listen/Port & port \\
/Component/Listen/Version & ipversion \\
/Component/Listen/NoDelay & nodelay \\
/Component/Listen/Timeout & timeout \\
/Component/Limit & limit \\
/Component/Limit.drop & drop \\
\midrule
\multicolumn{2}{c}{\textbf{TLS MCC}}\\
\midrule
/Component/KeyPath & x509\_user\_key \\
/Component/CertificatePath & x509\_user\_cert \\
/Component/CACertificatePath & x509\_cacert\_path \\
/Component/CACertificatesDir & x509\_cacert\_dir \\
/Component/CACertificatesDir.PolicyGlobus & policyglobus \\
/Component/ClientAuthn & clientauthn \\
/Component/VOMSCertTrustDNChain/VOMSCertTrustDN &  \\
/Component/VOMSCertTrustDNChain/VOMSCertTrustRegex &  \\
/Component/VOMSCertTrustDNChainsLocation & \\
/Component/Handshake & handshake \\
\bottomrule
\end{tabular}

 \lstset{
         basicstyle=\footnotesize\ttfamily,
 }

\section{XML Schemas}
\subsection{General Daemon Schema}
\lstinputlisting[language=xml]{base.xsd}

\subsection{Loader Schema}
\lstinputlisting[language=xml]{loader.xsd}

\subsection{TCP MCC Schema}
\lstinputlisting[language=xml]{tcp.xsd}

\subsection{TLS MCC Schema}
\lstinputlisting[language=xml]{tls.xsd}

\subsection{GSI MCC Schema}
\lstinputlisting[language=xml]{gsi.xsd}

\subsection{ARC Authorization Security Handler Schema}
\lstinputlisting[language=xml]{ArcAuthZ.xsd}

\subsection{UsernameToken Security Handler Schema}
\lstinputlisting[language=xml]{UsernameTokenSH.xsd}

\subsection{X.509 Token Security Handler Schema}
\lstinputlisting[language=xml]{X509TokenSH.xsd}

\subsection{SAML Token Security Handler Schema}
\lstinputlisting[language=xml]{SAMLTokenSH.xsd}

\subsection{ARC PDP Schema}
\lstinputlisting[language=xml]{ArcPDP.xsd}

\subsection{XACML PDP Schema}
\lstinputlisting[language=xml]{XACMLPDP.xsd}

\subsection{Delegation PDP Schema}
\lstinputlisting[language=xml]{DelegationPDP.xsd}

\subsection{Service Invoker PDP Schema}
\lstinputlisting[language=xml]{PDPServiceInvoker.xsd}

\subsection{Simple List PDP Schema}
\lstinputlisting[language=xml]{SimpleListPDP.xsd}

>>>>

\begin{center}
\small
\begin{tabular}{>{\ttfamily}l>{\ttfamily}l>{\ttfamily}l}
\toprule
\textrm{\textbf{XML element/attribute}} & \textrm{\textbf{INI tag}} & \textrm{\textbf{Default value}}\\
\midrule
/Server/PidFile & pidfile & /var/run/arched.pid\\
/Server/User & user & \textrm{None} \\
/Server/Group & group & \textrm{None} \\
/Server/Logger/File & logfile & /var/log/arched.log \\
/Server/Logger/Level & loglevel & WARNING \\
/Server/Logger/Maxsize & logmaxsize & \textrm{None} \\
/Server/Logger/Backups & logbackups & \textrm{None} \\
/ModuleManager/Path & libpath & \textrm{None} \\
/Plexer/next & endpointpattern & \textrm{None} \\
\midrule
\multicolumn{3}{c}{\textbf{TCP MCC}}\\
\midrule
/Component/Listen/Interface & interface & 0.0.0.0 \\
/Component/Listen/Port & port & 60000\\
/Component/Listen/Version & ipversion & \textrm{None} \\
/Component/Listen/NoDelay & nodelay & false\\
/Component/Listen/Timeout & timeout & \textrm{None}\\
/Component/Limit & limit & \textrm{None}\\
/Component/Limit.drop & drop & \textrm{None}\\
\midrule
\multicolumn{3}{c}{\textbf{TLS MCC}}\\
\midrule
/Component/KeyPath & x509\_host\_key & /etc/grid-security/hostkey.pem\\
/Component/CertificatePath & x509\_host\_cert & /etc/grid-security/hostcert.pem\\
/Component/CACertificatePath & x509\_cacert\_path & \textrm{None}\\
/Component/CACertificatesDir & x509\_cacert\_dir & /etc/grid-security/certificates\\
%/Component/CACertificatesDir.PolicyGlobus & policyglobus \\
/Component/ClientAuthn & clientauthn & true\\
%/Component/VOMSCertTrustDNChain/VOMSCertTrustDN &  \\
%/Component/VOMSCertTrustDNChain/VOMSCertTrustRegex &  \\
%Component/VOMSCertTrustDNChainsLocation & \\
/Component/Handshake & handshake & TLS\\
\bottomrule
\end{tabular}
\end{center}
